### 2017-11-11 vipassana-for-hackers.tex
fixing warnings... have not fixed hindi rendering (yet)

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{enumitem}
\setlist{noitemsep}

@@

I have drawn my personal spectrum for sample activities below.

\begin{figure}[h]
  \centering
  \includegraphics[width=11cm]{images/meditation-spectrum-1.jpeg}
  \caption{Sample meditation/meditative spectrum.}
  \label{fig:meditation-spectrum-1}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=11cm]{images/meditation-spectrum-3.jpeg}
  \caption{Sample meditation spectrum.}
  \label{fig:meditation-spectrum-3}
\end{figure}

@@

On that note, I feel I should introduce an absolutely fantastic RadioLab episode (\textit{Where Am I?} \cite{whereami}) which addresses this topic of ``other senses'' from the perspectives brought by modern Neuroscience. On the topic of lacking proprioception: ``We have words like `deaf' and `blind'. We do not have words for being deaf or blind to one's own body.'' In the Matrix, perhaps this is either a bug or a feature flag.

@@

Let us quickly revisit our third suspension of disbelief: ``dissolution of the body is a thing.'' Neuroscience tells us some interesting things about the nature of our sense of self and how it relates to our body. From ``Where Am I?'' \cite{whereami}:\\

\textbf{``The studies reported that people who had once been able-bodied and then became paralyzed felt… less. Less happy than able-bodied people, less sad than able-bodied people. Just less.''}\\

\textbf{``Our \textit{being} is rooted in a body-state. If I were able to remove from your brain, the representation of your body, you would not know that you were you.''}\\

@@

Such distractions are difficult to overcome, since they appear to replace consciousness and reality itself.\\

@@

There is a sketch in \textit{Where Am I?} \cite{whereami} about an arguing couple who must overcome their emotional temptation to get wound up by anger, ending in this wonderful quote:\\

\textbf{``Honey, don’t forget what the half-life is on the autonomic nervous system.''}\\

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength{\parindent}{2em}
\setlength{\parskip}{0.7em}
\setlist{noitemsep}

@@

I have drawn my personal spectrum for sample activities in Figure~\ref{fig:meditation-spectrum-1}.

\begin{figure}[H]
  \centering
  \includegraphics[width=11cm]{images/meditation-spectrum-1.jpeg}
  \caption{Sample meditation/meditative spectrum.}
  \label{fig:meditation-spectrum-1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=11cm]{images/meditation-spectrum-3.jpeg}
  \caption{Sample meditation spectrum.}
  \label{fig:meditation-spectrum-3}
\end{figure}

@@

On that note, I feel I should introduce an absolutely fantastic RadioLab episode (\textit{Where Am I?} \cite{whereami}) which addresses this topic of ``other senses'' from the perspectives brought by modern Neuroscience. On the topic of lacking proprioception:

\begin{quote}
  \textbf{We have words like `deaf' and `blind'. We do not have words for being deaf or blind to one's own body.}
\end{quote}

In the Matrix, perhaps this is either a bug or a feature flag.

@@

Let us quickly revisit our third suspension of disbelief: ``dissolution of the body is a thing.'' Neuroscience tells us some interesting things about the nature of our sense of self and how it relates to our body. From \textit{Where Am I?} \cite{whereami}:

\begin{quote}
  \textbf{The studies reported that people who had once been able-bodied and then became paralyzed felt… less. Less happy than able-bodied people, less sad than able-bodied people. Just less.}
\end{quote}

\begin{quote}
  \textbf{Our \textit{being} is rooted in a body-state. If I were able to remove from your brain, the representation of your body, you would not know that you were you.}
\end{quote}

@@

Such distractions are difficult to overcome, since they appear to replace consciousness and reality itself.

@@

There is a sketch in \textit{Where Am I?} \cite{whereami} about an arguing couple who must overcome their emotional temptation to get wound up by anger, ending in this wonderful quote:

\begin{quote}
  \textbf{Honey, don’t forget what the half-life is on the autonomic nervous system.}
\end{quote}
